Hierarchy Builder: algebraic~hierarchies made easy in Coq with Elpi

### 2020-04-26 hb.tex
a last check on section names
my other 2 C ;)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\HB{} language}\label{sec:language}

@@

\subsection{\HB{} \mixins{}, \factories{} and instances}
\label{sec:hb-mixins-factories}

@@

\Mixins{} are declared by the user as the fundamental building blocks of
a hierarchy. As the next proposition shows they shall not be regarded as
different from regular \factories{}, since they are a special cases.

@@

\begin{command} to declare a new mixin:
\begin{coqcode}
#\hbmixin{}# Record M T of #$f_1\ \ldots\ f_n$# := { .. }.
\end{coqcode}
  Declares the record \coq{M} inside an homonymous module \coq{M}.
  The record \coq{M.M} depends on the \mixins{}
  \(\requires{}(\coq{M}) = \dep{}(\coq{M}) =
  \provides{}^\star\left(\enum{f_1}{f_n}\right)\)
  and is registered both as a \mixin{} and a \factory{}. Finally It exports an
  \phantterm{} \coq{M.Build} and a notation
  \coq{M} standing for \coq{M.M}, so that the module name can be used to
  denote the homonymous record it contains.
\end{command}

@@

  Definition #$b_{n+1}$# : #$f_{n+1}$# T .. := ...
  #\hbinstance{}# T #$b_{n+1}$#.
  ..
  Definition #$b_{n+k}$# : #$f_{n+k}$# T .. := ...
  #\hbinstance{}# T #$b_{n+k}$#.
#\hbend{}#.
\end{coqcode}
  Declares the record \coq{F} inside an homonymous module \coq{F}.
  The record \coq{F.F} depends on the mixins
  \(\requires{}(\coq{M}) =
  \provides{}^\star\left(\enum{f_1}{f_n}\right)\) and is registered
  as a factory.  It exports an
  \phantterm{} \coq{F.Build.} and a notation
  \coq{F} standing for \coq{F.F}, so that the module name can be used to
  denote the homonymous record it contains.
  Finally it uses the \factoryinstances{}
  \(b_{n+1}, \ldots, b_{n+k}\) provided by the user in order to derive
  \mixinbuilders{}, so that
  \(\provides{}(\coq{F}) = \provides{}^\star\left(\enum{f_{n+1}}{f_{n+k}}\right).\)
  It is thus necessary that
  \(\requires{}^\star\left(\enum{f_{n+1}}{f_{n+k}}\right) \subseteq
  \provides{}^\star\left(\enum{f_1}{f_n}\right).\)
\end{commands}

Note that the \(b_i\) are not \mixinbuilders{} since their return types
are not necessarily \mixins{}, but could be \factories{}. However, since all
\factories{} provide \mixins{} through \mixinbuilders{}, we
can obtain \mixinbuilders{} out of each \(b_i\) by function composition.

\subsection{\HB{} classes and structures}
\label{sec:hb-class-struct}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The implementation in Coq-Elpi}\label{sec:implementation}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The \HB{} language}\label{sec:language}

@@

\subsection{\Mixins{}, \factories{} and instances}
\label{sec:hb-mixins-factories}

@@

\Mixins{} are declared by the user as the fundamental building blocks of
a hierarchy. As the next proposition shows they shall not be regarded as
different from regular \factories{}, since they are a special case.

@@

\begin{command} to declare a new mixin:
\begin{coqcode}
#\hbmixin{}# Record M T of #$f_1\ \ldots\ f_n$# := { .. }.
\end{coqcode}
  Declares the record \coq{axioms} inside a module \coq{M}.
  This record \coq{M.axioms} depends on the \mixins{}
  \(\requires{}(\coq{M.axioms}) = \dep{}(\coq{M.axioms}) =
  \provides{}^\star\left(\enum{f_1}{f_n}\right)\)
  and is registered both as a \mixin{} and a \factory{}. Finally It exports an
  \phantterm{} \coq{M.Build} and a notation
  \coq{M} standing for \coq{M.axioms}, so that the module name can be used to
  denote the \coq{axioms} record it contains.
\end{command}

@@

  Definition #$b_{n+1}$# : #$f_{n+1}$# T .. := ...
  #\hbinstance{}# T #$b_{n+1}$#.
  ..
  Definition #$b_{n+k}$# : #$f_{n+k}$# T .. := ...
  #\hbinstance{}# T #$b_{n+k}$#.
#\hbend{}#.
\end{coqcode}
  Declares the record \coq{axioms} inside a module \coq{F}.
  This record \coq{F.axioms} depends on the mixins
  \(\requires{}(\coq{F.axioms}) =
  \provides{}^\star\left(\enum{f_1}{f_n}\right)\) and is registered
  as a factory.  It exports an
  \phantterm{} \coq{F.Build} and a notation
  \coq{F} standing for \coq{F.axioms}, so that the module name can be used to
  denote the \coq{axioms} record it contains.
  Finally it uses the \factoryinstances{}
  \(b_{n+1}, \ldots, b_{n+k}\) provided by the user in order to derive
  \mixinbuilders{}, so that
  \(\provides{}(\coq{F}) = \provides{}^\star\left(\enum{f_{n+1}}{f_{n+k}}\right).\)
  It is thus necessary that
  \(\requires{}^\star\left(\enum{f_{n+1}}{f_{n+k}}\right) \subseteq
  \provides{}^\star\left(\enum{f_1}{f_n}\right).\)
\end{commands}

Note that the \(b_i\) are not \mixinbuilders{} since their return types
are not necessarily \mixins{}, but could be \factories{}. However, since all
\factories{} provide \mixins{} through \mixinbuilders{}, we
obtain \mixinbuilders{} out of each \(b_i\) by function composition.

\subsection{Classes and structures}
\label{sec:hb-class-struct}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The implementation of \HB{} in Coq-Elpi}\label{sec:implementation}
